The title

### 2018-10-23 Untitled.tex
convert to papaja, temporary references fix

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={The development of infants' responses to mispronunciations - A Meta-Analysis},
            pdfauthor={Katie Von Holzen~\& Christina Bergmann},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{The development of infants' responses to mispronunciations - A
Meta-Analysis}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Katie Von Holzen\textsuperscript{1,2}~\& Christina
Bergmann\textsuperscript{3,4}}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \date{}
  \predate{}\postdate{}

\shorttitle{Mispronunciation Meta-Analysis}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Language Development Laboratory, University of Maryland, USA\\\textsuperscript{2} Laboratoire Psychologie de la Perception, Université Paris Descartes\\\textsuperscript{3} Max Planck Institute for Psycholinguistics, Nijmegen, the Netherlands\\\textsuperscript{4} LSCP, Departement d'Etudes Cognitives, ENS, EHESS, CNRS, PSL Research University}
\keywords{keywords\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\authornote{

Correspondence concerning this article should be addressed to Katie Von
Holzen, 0221A LeFrak Hall, University of Maryland, College Park, MD
20742. E-mail:
\href{mailto:katie.m.vonholzen@gmail.com}{\nolinkurl{katie.m.vonholzen@gmail.com}}}

@@

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle

\section{Introduction}\label{introduction}

Acquiring a first language means that young learners are solving a host
of tasks in a short amount of time. As infants develop into toddlers
during their second and third years they learn new words in earnest
while simultaneously refining their knowledge about the sounds that make
up these words. Before children can correctly pronounce a word, they
already show evidence of sensitivity to slight variations in the
phonological form of that word. This mispronunciation sensitivity
reflects the specificity with which infants represent the phonological
information of familiar words and are sensitive to changes that might
signal a change in word meaning. As infants continue to develop into
expert language users, their language processing matures and becomes
more efficient. In a mature phono-lexical system, word recognition must
balance flexibility to slight variation (e.g., speaker identity,
accented speech) while distinguishing between phonetic details that
differentiate words in their native language (e.g.~cat-hat). In this
paper, we aggregate and analyze the almost 20 years of literature
investigating mispronunciation sensitivity in infants in an attempt to
uncover its characteristics and the trajectory of its development.

At the turn of the millenia, infant language acquisition researchers had
established that during their first years of life, infants are sensitive
to changes in the phonetic detail of newly segmented words (Jusczyk \&
Aslin, 1995) and learned minimal pairs (Stager \& Werker, 1997).
Furthermore, when presented with familiar image pairs, children fixate
on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg,
\& McRoberts, 1998). Swingley and Aslin (2000) were the first to tie
these lines of research together and investigate mispronunciation
sensitivity in infant familiar word recognition: Children aged 18 to 23
months learning American English were presented with pairs of images
(e.g.~baby, dog) and their eye movements to each image were coded
offline. On \enquote{correct} trials, children heard the correct label
for one of the images (e.g.~baby). On \enquote{mispronounced} trials,
children heard a mispronounced label of one of the images (e.g.~vaby).
Mean proportion of fixation to the target image (here: a baby) was
calculated for both correct and mispronounced trials by dividing the
target looking time by the sum of total looking time to both target and
a distractor (proportion of target looking or PTL). Mean fixations in
correct trials were significantly greater than in mispronounced trials,
although looks to the target were significantly greater than chance in
both types of trials. We refer to this pattern of a difference between
looks to correct and mispronounced words as \emph{mispronunciation
sensitivity} and of looks to the target image above chance as
\emph{recognition}. Swingley and Aslin (2000) concluded that already
before the second birthday, children represent words with sufficient
detail to be sensitive to mispronunciations.

The study of Swingley and Aslin (2000) as well as subsequent studies
examining mispronunciation sensitivity address two complementary
concepts in early phonological development: \emph{phonological
constancy} and \emph{phonological distinctiveness}. Phonological
constancy is the ability to accept phonological variation across
different instances of a word, as long as the variation does not
compromise the overall identity of the word. For example, different
speakers - particularly across genders and accents - produce the same
word with notable acoustic variation, although the word remains the
same. In contrast, phonological distinctiveness describes the ability to
differentiate between different words that happen to be phonologically
similar, such as bad/bed or cat/hat. To successfully recognize words,
infants must therefore simultaneously use both phonological constancy
and distinctiveness to determine where phonological variation is
appropriate and where it changes a word's meaning.

In the current study, we focus on infants' developing ability to
correctly apply the principles of phonological distinctiveness and
constancy by using a meta-analytic approach to investigate
mispronunciation sensitivity. Considering that infants are sensitive to
mispronunciations and that, in general, their processing matures with
development, we examine the shape of mispronunciation sensitivity over
the course of the second and third year. There are three distinct
possibilities how mispronunciation sensitivity might change as infants
become native speakers, which are all respectively predicted by
theoretical accounts and supported by single studies. By aggregating all
publicly available evidence using meta-analysis, we can examine
developmental trends making use of data from a much larger and diverse
sample of infants. Before we outline the meta-analytical approach and
its advantages in detail, we first discuss the proposals this study
seeks to disentangle and the data supporting each of the accounts.

Young infants may begin cautiously in their approach to word
recognition, rejecting any phonological variation in familiar words and
only later learning to accept appropriate variability. According to the
Perceptual Attunement account, this describes a shift away from specific
native phonetic patterns to a more mature understanding of the abstract
phonological structure of words (Best 1994, 1995). This shift is
predicted to coincide with the vocabulary spurt around 18 months, and is
therefore related to vocabulary growth. In this case, we would expect
the size of mispronunciation sensitivity to be larger at younger ages
and \emph{decrease} as the child matures and learn more words, although
children continue to detect mispronunciations. Indeed, young infants are
less likely than older infants to demonstrate recognition of familiar
words (Best, Tyler, Gooding, Orlando, \& Quann, 2009; Mulak, Best, \&
Tyler, 2013) or learn new words (Schmale, Hollich, \& Seidl, 2011) from
accented speakers.

According to a different theoretical framework, young infants may
instead begin with phonologically broad representations for familiar
words and only refine their representations as language experience
accumulates. PRIMIR (Processing Rich Information from Multidimensional
Interactive Representations; Curtin \& Werker, 2007; Werker \& Curtin,
2005; Curtin, Byers-Heinlein, \& Werker, 2011) describes the development
of phonemic categories emerging as the number of word form-meaning
linkages increases. Vocabulary growth, therefore, promotes more detailed
phonological representations in familiar words. Following this account,
we predict an \emph{increase} in mispronunciation sensitivity as infants
mature and add more words to their growing lexicon.

Finally, sensitivity to mispronunciation may not be modulated by
development at all. Infants' overall language processing becomes more
efficient, but their sensitivity to mispronunciations may not change.
Across infancy and toddlerhood, mispronunciations would thus be detected
and lead to less looks at a target than correct pronunciations, but the
size of this effect would not change, nor be related to vocabulary size.
This pattern is not predicted by any mainstream theory of language
acquisition, but for completeness we mention it here.

Research following the seminal study by Swingley and Aslin (2000) has
extended mispronunciation sensitivity to infants as young as 12 months
(Mani \& Plunkett, 2010), indicating that from early stages of the
developing lexicon onwards, infants can and do detect mispronunciations.
Regarding the change in mispronunciation sensitivity over development,
however, only a handful of studies have compared more than one age group
on the same mispronunciation task (see Table X), making the current
meta-analysis very informative. One study has found evidence for infants
to become \emph{less} sensitive to mispronunciations as children
develop. Mani and Plunkett (2011) presented 18- and 24-month-olds with
mispronunciations varying in the number of features changed (see below
for a discussion of the role of features). 18-month-olds were sensitive
to mispronunciations, regardless of the number of features changed.
24-month-olds, in contrast, fixated the target image equally for both
correct and 1-feature mispronounced trials, although they were sensitive
to larger mispronunciations. In other words, for 1-feature
mispronunciations at least, sensitivity decreased from 18 to 24 months,
providing support to the prediction that mispronunciation sensitivity
may decrease with development.

In contrast, other studies have found evidence for \emph{greater}
mispronunciation sensitivity as children develop. More precisely, the
difference in target looking for correct and mispronounced trials is
smaller in younger infants and grows as infants develop. Mani and
Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British
English; although all three groups were sensitive to mispronunciations,
15-month-olds showed a less robust sensitivity. An increase in
sensitivity to mispronunciations has also been found from 20 to 24
months (van der Feest \& Fikkert, 2015) and 15 to 18 months (Altvater
Mackensen et al., 2013) in Dutch infants, as well as German infants from
22 to 25 months (Altvater-Mackensen, 2010). Furthermore, van der Feest
and Fikkert (2015) found that sensitivity to specific kinds of
mispronunciations develop at different ages depending on language
infants are learning. In other words, the native language constraints
which \emph{kinds} of mispronunciations infants are sensitive to first,
and that as infants develop, they become sensitive to other
mispronunciations. These studies award support to the prediction that
mispronunciation sensitivity improves with development.

Finally, some studies have found no difference in mispronunciation
sensitivity at different ages. Swingley and Aslin (2000) tested infants
over a wide age range of 5 months (18 to 23 months). They found that age
correlated with target fixations for both correct and mispronounced
labels, whereas the difference between the two (mispronunciation effect)
did not. This suggests that as children develop, they are more likely to
look at the target in the presence of a mispronounced label and that age
is not related to mispronunciation sensitivity. A similar response
pattern has been found for British English learning infants aged between
18 and 24 months (Bailey \& Plunkett, 2002) as well as younger
French-learning infants at 12 and 17 months (Zesiger, Lozeron, Levy, \&
Frauenfelder, 2012). These studies award support to the prediction that
mispronunciation sensitivity does not change with development.

Why would mispronunciation sensitivity change as infants develop, and
would it increase or decrease? The main hypothesis is related to
vocabulary growth. Both the Perceptual Attunement (Best, 1994; 1995) and
PRIMIR (Curtin \& Werker, 2007; Werker \& Curtin, 2005; Curtin,
Byers-Heinlein, \& Werker, 2011) accounts situate a change in
mispronunciation sensitivity occurring along with an increase in
vocabulary size, particularly with the vocabulary spurt at about 18
months. Knowing more words helps infants shift their focus to the
relevant phonetic dimensions needed for word recognition. On the one
hand, a smaller lexicon does not require full specification to
differentiate between words; as more phonologically similar words are
learned, so does the need to have fully detailed representations for
those words (Charles-Luce \& Luce, 1995). On the other hand, a growing
vocabulary is also related to more experience or familiarity with words,
which may sharpen the detail of their representation (Barton, 1980).

Yet, the majority of studies examining a potential association between
mispronunciation sensitivity and vocabulary size have concluded that
there is no relationship (Swingley \& Aslin 2000; 2002; Bailey \&
Plunkett, 2002; Zesiger, Lozeron, Levy, \& Frauenfelder, 2012; Swingley,
2009; Ballem \& Plunkett, 2005; Mani \& Plunkett, 2007; Mani, Coleman,
\& Plunkett, 2008). One notable exception comes from Mani and Plunkett
(2010: keps and tups). Here, 12-month-old infants were divided into a
low vocabulary and high vocabulary group based group median vocabulary
size. High vocabulary infants showed greater sensitivity to vowel
mispronunciations than low vocabulary infants, although this was not the
case for consonant mispronunciations. Taken together, although receiving
considerable support from theories of phono-lexical processing in
language acquisition, there is very little evidence for a role of
vocabulary size in mispronunciation sensitivity. In our current
meta-analysis, we include the relationship between mispronunciation
sensitivity and vocabulary size to further disentangle the disconnect
between theory and experimental results.

Next to this core theoretically relevant investigation of the shape of
development of infants' mispronunciation sensitivity, we take the
opportunity of a systematic aggregation of data to address open
questions regarding differences in experiment design and whether changes
in procedure and stimuli tap into significantly different aspects of
infants' ability to detect mispronunciations.

In designing their mispronunciation stimuli, Swingley and Aslin (2000)
chose consonant mispronunciations that were likely to confuse adults
(Miller \& Nicely, 1955). Subsequent research has settled on
systematically modulating phonemic features to achieve mispronunciations
of familiar words. By utilizing mispronunciations consisting of phonemic
changes, these experiments examine infants' sensitivity to factors that
change the identity of a word on a measurable level (i.e.~1-feature,
2-features, 3-features, etc.). The importance of controlling for the
degree of phonological mismatch, as measured by number of features
changed, is further highlighted by studies that find graded sensitivity
to both consonant (White \& Morgan, 2008) and vowel (Mani \& Plunkett,
2011) feature changes.

Although most research examining sensitivity to mispronunciations
follows a similar design, there are some notable differences. For
example, Swingley and Aslin (2000) presented infants with pairs of
familiar images, one serving as the labeled target and one as the
unlabeled distractor. In contrast, White and Morgan (2008; see also Mani
\& Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented
infants with pairs of familiar (labeled target) and unfamiliar
(unlabeled distractor) objects. By using an unfamiliar object as a
distractor, the infant is presented with a viable option onto which the
mispronounced label can be applied (Halberda, 2003; Markman, Wasow, \&
Hansen, 2003). Infants ages 24 and 30 months associate a novel label
with an unfamiliar object, although only 30-month-olds retained this
label-object pairing (Bion, Borovsky, and Fernald, 2013). In contrast,
18-month-olds did not learn to associate a novel label with an
unfamiliar object, providing evidence that this ability is developing
from 18 to 30 months. We may find that if mispronunciation sensitivity
changes as children develop, that this change is modulated by whether
the distractor used is familiar or unfamiliar. Although mispronunciation
sensitivity in the presence of a familiar compared to unfamiliar
distractor has not been directly compared, the baseline preference for
familiar compared to novel stimuli is also thought to change as infants
develop (Hunter \& Ames, 1988). Furthermore, young children have been
found to look longer at objects for which they know the name, compared
to objects of an unknown name (Schafer \& Plukett, 1998). In other
words, in absentia of a label, infants may be more or less likely to
fixate on an unfamiliar object. To account for inherent preferences to
the target or distractor image, mispronunciation experiments typically
compare the increase in fixations to the target image from a silent
baseline to post-labeling or present the same yoked pairs of target and
distractor images in in both a correct and mispronounced labelling
context. Considering this evidence, we may expect that in older, but not
younger, children, the presence of an unfamiliar distractor may lead to
greater mispronunciation sensitivity than in the presence of a familiar
distractor.

Furthermore, when presenting infants with a familiar distractor image,
some studies control the phonological overlap between the labels for the
target and distractor. For example, when examining sensitivity to a
mispronunciation of the target word \enquote{dog}, the vowel
mispronunciation \enquote{dag} would be paired with a distractor image
that shares onset overlap, such as \enquote{duck}. This ensures that
infants can not use the onset of the word to differentiate between the
target and distractor images (Fernald, Swingley, \& Pinto, 2001).
Instead, infants must pay attention to the mispronounced phoneme in
order to successfully detect the change. The influence of distractor
overlap also depends on the position of the mispronunciation in the
word, which can be at word onset, medial, or final positions. Models of
spoken word processing place more or less importance on the position of
a phoneme in a word. The COHORT model (Marslen-Wilson \& Zwitserlood,
1989) describes lexical access in one direction, with the importance of
each phoneme decreasing as its position comes later in the word. In
contrast, the TRACE model (McClelland \& Elman, 1986) describes lexical
access as constantly updating and reevaluating the incoming speech input
in the search for the correct lexical entry, and therefore can recover
from word onset and to a lesser extent medial mispronunciations.

TRACE has also been used to model infants' sensitivity to
mispronunciation location (Mayor \& Plunkett, 2014), finding that as
lexicon size increases, so does sensitivity to onset mispronunciations,
whereas medial mispronunciations do not experience similar growth. In
early language acquisition, infants typically know more consonant
compared to vowel onset words. When tested on their recognition of
familiar words, therefore, younger infants would show greater
sensitivity to onset mispronunciations, which are frequently consonant
mispronunciations. The prevalence of consonant onset words may
contribute to the finding that consonants carry more weight in lexical
processing (C-bias; see Nazzi, Poltrock, \& Von Holzen, 2016 for a
recent review). In mispronunciation sensitivity, this would translate to
consonant mispronunciations impairing word recognition to a greater
degree than vowel mispronunciations. Yet, the handful of studies
directly comparing sensitivity to consonant and vowel mispronunciations
mostly find symmetry as opposed to an asymmetry between consonants and
vowels. English-learning 12-, 15-, 18-, and 24-month-olds (Mani \&
Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds
(Hojen et al., unpublished) demonstrate similar sensitivity to consonant
and vowel mispronunciations. One study did find weak evidence for
greater sensitivity to consonant compared to vowel mispronunciations
(Swingley, 2016). The English-learning infants tested by Swingley were
older than previous studies (mean age 28 months). In word learning, the
C-bias has been found to develop later in English learning infants
(Floccia, Nazzi, Delle Luche, Poltrock, \& Goslin, 2014; Nazzi, Floccia,
Moquet, \& Butler, 2009). In the current meta-analysis, we attempt to
synthesize studies examining sensitivity to consonant and vowel
mispronunciations across different ages to determine whether infants
generally exhibit more sensitivity to consonant compared to vowel
mispronunciations in familiar word recognition as predicted by a learned
account of C-bias emergence (Floccia et al., 2014; Keidel et al., 2007;
Nazzi et al., 2016). We further examine the impact of language family on
mispronunciation sensitivity to consonants and vowels, as C-bias
emergence has been found to have a different developmental trajectory
for Romance (French, Italian) compared to Germanic (British English,
Danish) languages (Nazzi et al., 2016).

{[}KATIE{]} Christina had noted something to herself for this paragraph:
Subset by language?

Finally, mispronunciation sensitivity in infants has been examined in
many different languages, such as English, Spanish, French, Dutch,
German, Catalan, Danish, and Mandarin Chinese (see Summary\_Table).
Infants learning different languages have different ages of acquisition
for words in their early lexicon, leaving direct comparisons between
languages within the same study difficult and as a result rare. Yet,
studies testing infants from different language backgrounds on similar
sets of stimuli find similar sensitivity to mispronunciations
(Ramon-Casas et al., 2009; Ramon-Casas \& Bosch, 2010). Although we do
not explicitly compare overall mispronunciation sensitivity by language
(although see previous paragraph for rationale to test by language
family), we assess evidence of mispronunciation sensitivity from many
different languages using a meta-analytic approach.

Taken together, the studies we have reviewed begin to paint a picture of
the development of mispronunciation sensitivity. Each study contributes
one separate brushstroke and it is only by examining all of them
together that we can achieve a better understanding. In our analysis, we
examine the factors modulating the development of mispronunciation
sensitivity, which are both of theoretical and practical importance.
Meta-analyses can not only help us summarize the current state of
research, but can also help us evaluate theories to drive future
research and make hands-on recommendations for experiment planning.

@@

The present meta-analysis was conducted with maximal transparency and
reproducibility in mind. To this end, we provide all data and analysis
scripts on the supplementary website (\url{https://osf.io/rvbjs/}) and
open our meta-analysis up for updates (Tsuji, Bergmann, \& Cristia,
2014). The most recent version is available via the website and the
interactive platform MetaLab (metalab.stanford.edu; Bergmann et al.,
2018). Since the present paper was written with embedded analysis
scripts in R {[}@R{]}, it is always possible to re-analyze an updated
dataset. In addition, we follow the Preferred Reporting Items for
Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make the
corresponding information available as supplementary materials (Moher,
Liberati, Tetzlaff, Altman \& PRISMAGroup, 2009). Figure X plots our
PRISMA flowchart.

{[}Figure X. PRISMA Flowchart.{]}
(figures/PRISMA\_MA\_Mispronunciation.png)

\subsection{Study Selection}\label{study-selection}

\begin{tabular}{l|l|l|l|l|l|l|l}
\hline
Paper & Age & Vocabulary & \# Features & Distractor & Distractor name overlap & MP Position & MP Type\\
\hline
Altvater-Mackensen (2010) & 22, 25 & None & 1 & Familiar, Unfamiliar & onset, novel & onset, onset/medial & consonant\\
\hline
Altvater-Mackensen et al. (2014) & 18, 25 & None & 0, 1 & Familiar & onset & onset & consonant\\
\hline
Bailey \& Plunkett (2002) & 18, 24 & Comprehension & 0, 1, 2 & Familiar & no & onset & consonant\\
\hline
Bergelson \& Swingley (2017) & 7, 9, 12, 6 & None & 0, NA & Familiar & no & onset/medial & vowel\\
\hline
Bernier \& White 2017 & 21 & None & 0, 1, 2, 3 & Unfamiliar & novel & onset & consonant\\
\hline
Delle Luche et al. (2015) & 20, 19 & None & 0, 1 & Familiar & onset & onset & consonant\_and\_vowel\\
\hline
Durrant et al. (2014) & 19, 20 & None & 0, 1 & Familiar & onset & onset & consonant\_and\_vowel\\
\hline
Hoehle et al. 2006 & 18 & None & 1 & Familiar & no & onset & consonant\\
\hline
Hojen et al. & 20 & Comprehension/Production & 2\_3 & Familiar & coda, onset & onset/medial, coda/medial & consonant\_and\_vowel, vowel, consonant\\
\hline
Mani \& Plunkett 2007 & 15, 18, 24, 14, 21 & Comprehension/Production & 0, 1\_2, 1 & Familiar & onset & onset & vowel, consonant\_and\_vowel, consonant\\
\hline
Mani \& Plunkett 2010 & 12 & Comprehension & 0, 1 & Familiar & onset & medial, onset & vowel, consonant\\
\hline
Mani \& Plunkett 2011 & 23, 17 & None & 0, 1\_2\_3, 1, 2, 3 & Unfamiliar & novel & medial & vowel\\
\hline
Mani, Coleman, \& Plunkett (2008) & 18 & Comprehension/Production & 0, 1 & Familiar & onset & medial & vowel\\
\hline
Ramon-Casas \& Bosch 2010 & 24, 25 & None & NA & Familiar & no & medial & vowel\\
\hline
Ramon-Casas et al. 2009 & 21, 20 & Production & NA & Familiar & no & medial & vowel\\
\hline
Ren \& Morgan, in press & 19 & None & 0, 1 & Unfamiliar & no & onset, coda & consonant\\
\hline
Skoruppa et al. 2013 & 24 & None & 0, 1 & Unfamiliar & onset/medial & coda & consonant\\
\hline
Swingley (2009) & 17 & Comprehension/Production & 0, 1 & Familiar & no & onset, coda & consonant\\
\hline
Swingley (2016) & 27, 28 & Production & 0, 1 & Unfamiliar & novel & onset/medial & consonant\_and\_vowel, consonant, vowel\\
\hline
Swingley \& Aslin (2000) & 20 & Comprehension & 0, 1 & Familiar & no & onset & consonant\_and\_vowel\\
\hline
Swingley \& Aslin (2002) & 15 & Comprehension/Production & 0, 1, 2 & Familiar & no & onset/medial & consonant\_and\_vowel\\
\hline
Swingley 2003 & 19 & Comprehension/Production & 0, 1 & Familiar & onset & onset, medial & consonant\\
\hline
Tamasi (2016) & 30 & None & 0, 1, 2, 3 & Unfamiliar & novel & onset & consonant\\
\hline
Tao \& Qinmei 2013 & 12 & None & NA & Familiar & no & NA & tone\\
\hline
Tao et al. 2012 & 16 & Comprehension & NA & Familiar & no & NA & tone\\
\hline
van der Feest \& Fikkert, 2015 & 24, 20 & None & 0, 1 & Familiar & onset & onset & consonant\\
\hline
van der Feest \& Johnson, 2016 & 24 & None & 0, 1 & Familiar & onset & onset & consonant\\
\hline
Wewalaarachchi et al. 2017 & 24 & None & 0, 1 & Unfamiliar & novel & onset/medial/coda & consonant\_vowel\_tone, vowel, consonant, tone\\
\hline
White \& Aslin (2011) & 18 & None & 1 & Unfamiliar & novel & medial & vowel\\
\hline
White \& Morgan (2008) & 18, 19 & None & 0, 1, 2, 3 & Unfamiliar & novel & onset & consonant\\
\hline
Zesiger \& Johr 2011 & 14 & None & 0, 1 & Familiar & no & onset, medial & consonant, vowel\\
\hline
Zesiger et al. (2012) & 12, 19 & Comprehension/Production & 0, 1, 2 & Familiar & no & onset & consonant\\
\hline
\end{tabular}

{[}KATIE{]} THIS TABLE IS DEFINITELY NOT FINISHED! {[}CHRISTINA
suggestions: N features should be a range and exclude 0; we could
abbreviate Comperehension/Production to Comp./Prod.,
etcetc{]}{[}KATIE{]} I'll think about how to implement that! Might end
up having to adjust the table by hand, there is a lot of variation
between studies.

We first generated a list of potentially relevant items to be included
in our meta-analysis by creating an expert list. This process yielded
110 items. We then used the google scholar search engine to search for
papers citing the original Swingley \& Aslin (2000) publication. This
search was conducted on 22 September, 2017 and yielded 288 results. We
screened the 398 items, removing 99 duplicate items. We screened
remaining 299 items for their title and abstract to determine whether it
met the following inclusion criteria: (1) original data was reported;
(2) the experiment examined familiar word recognition; (3) infants
studied were under 36-months-of-age; (4) the dependent variable was
derived from proportion of looks to a target image versus a distractor
in a eye movement experiment; 5) the stimuli were auditory speech. The
final sample (n = \emph{32}) consisted of 27 journal articles, 1
proceedings paper, 2 thesis, and 2 unpublished reports. We will refer to
these items collectively as papers. Table 1 (Summary Table) provides an
overview of all papers included in the present meta-analysis.

\begin{tabular}{l|r|r}
\hline
Publication Type & \# Items & \# Effect Sizes\\
\hline
dissertation & 2 & 17\\
\hline
gray paper & 2 & 14\\
\hline
paper & 27 & 216\\
\hline
proceedings & 1 & 4\\
\hline
\end{tabular}

\subsection{Data Entry}\label{data-entry}

The 32 papers we identified as relevant were then coded with as much
detail as possible (Tsuji, Bergmann, \& Cristia, 2014; Bergmann et al.,
2018). For each experiment (note that a paper typically has multiple
experiments), we entered variables describing the publication,
population, experiment design and stimuli, and results. For the present
analyses, we focus on the following characteristics:\\
1 Condition: Were words mispronounced or not;\\
2 Mean age reported per group of infants, in days;\\
3 Vocabulary size, measured by a standardized questionnaire or list;\\
4 Size of mispronunciation, measured in features changed;\\
5 Distractor familiarity: familiar or unfamiliar;\\
6 Phonological overlap between target and distractor: onset,
onset/medial, rhyme, none, novel word;\\
7 Position of mispronunciation: onset, medial, offset, or mixed;\\
8 Type of mispronunciation: consonant, vowel, or both.

We separated out conditions according to whether or not the target word
was mispronounced to be able to investigate infants' looking to the
target picture separated by whether or not words were mispronounced as
well as their mispronunciation sensitivity, which is the difference
between looks to the target in correct and mispronounced trials. When
the same infants were further exposed to multiple mispronunciation
conditions and the results were reported separately in the paper, we
also entered each condition as a separate row (e.g., consonant versus
vowel mispronunciations; Mani \& Plunkett, 2007). The fact that the same
infants contributed data to multiple rows (minimally those containing
information on correct and mispronounced trials) leads to shared
variance across effect sizes, which we account for in our analyses (see
next section). We will call each row a record; in total there were 251
records in our data.

@@

\begin{tabular}{l|r|r}
\hline
Type of comparison & \# Papers & \# Effect Size\\
\hline
post-naming compared to pre-naming phase & 10 & 29\\
\hline
post-naming phase compared with chance (=50\%) & 9 & 23\\
\hline
post-pre difference score compared with chance (=0) & 13 & 52\\
\hline
\end{tabular}

>>>>

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={The title},
            pdfauthor={First Author~\& Ernst-August Doelle},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{The title}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{First Author\textsuperscript{1}~\& Ernst-August
Doelle\textsuperscript{1,2}}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \date{}
  \predate{}\postdate{}

\shorttitle{Title}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}
\keywords{keywords\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\authornote{Add complete departmental affiliations for each
author here. Each new line herein must be indented, like this line.

Enter author note here.

Correspondence concerning this article should be addressed to First
Author, Postal address. E-mail:
\href{mailto:my@email.com}{\nolinkurl{my@email.com}}}

@@

\begin{document}
\maketitle

@@

We report how we determined our sample size, all data exclusions (if
any), all manipulations, and all measures in the study.

\subsection{Participants}\label{participants}

\subsection{Material}\label{material}

\subsection{Procedure}\label{procedure}

@@
